MCC Kids Model Predictions

### 2019-03-09 papers/full_paper/models.Rmd
clean version models with non parametric model predictions for kids

  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})

@@

    var noise = logistic(noise_int + noise_slope * (row.age_num - row.minage))

@@

    observe(noisyModelPredictions, row.correct_inf)

    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]

@@

 return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})

```{r}
# child_ex3_pragm_model<- webppl(
#   program_code = paste(rsaUtils, childRsaModel, child.ex3.rsa.predictions , sep='\n'),
#   data =list(ex3data = ex3_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 3000, burn = 1000, verbose = T)
# )%>%
#   saveRDS("../../stats/saves/child_ex3_pragm_model.rds")

child_ex3_pragm_model <- readRDS("../../stats/saves/child_ex3_pragm_model.rds")

child_ex3_pragm_model_predictions <- child_ex3_pragm_model%>%
  filter(!(Parameter %in% c("noise_int","noise_slope")))  %>%
  separate(Parameter, into = c("age","speaker", "alignment"), sep="/")%>%
  mutate(model="pragmatic")%>%
  group_by(model,age,speaker,alignment)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))

child_ex3_pragm_model_noise <- child_ex3_pragm_model %>%
  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
  group_by(Parameter)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

@@

 return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})

```{r}
# child_ex3_prior_only_model<- webppl(
#   program_code = paste(rsaUtils, childRsaModel, child.ex3.prior.only.predictions , sep='\n'),
#   data =list(ex3data = ex3_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 3000, burn = 1000, verbose = T)
# )%>%
#   saveRDS("../../stats/saves/child_ex3_prior_only_model.rds")

child_ex3_prior_only_model <- readRDS("../../stats/saves/child_ex3_prior_only_model.rds")

child_ex3_prior_only_model_predictions <- child_ex3_prior_only_model%>%
  filter(!(Parameter %in% c("noise_int","noise_slope")))  %>%
  separate(Parameter, into = c("age","speaker", "alignment"), sep="/")%>%
  mutate(model="prior_only")%>%
  group_by(model,age,speaker,alignment)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))

child_ex3_prior_only_model_noise <- child_ex3_prior_only_model %>%
  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
  group_by(Parameter)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

@@

 return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})

```{r}
# child_ex3_flat_prior_model<- webppl(
#   program_code = paste(rsaUtils, childRsaModel, child.ex3.rsa.predictions , sep='\n'),
#   data =list(ex3data = ex3_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 3000, burn = 1000, verbose = T)
# )%>%
#   saveRDS("../../stats/saves/child_ex3_flat_prior_model.rds")

child_ex3_flat_prior_model <- readRDS("../../stats/saves/child_ex3_flat_prior_model.rds")

child_ex3_flat_prior_model_predictions <- child_ex3_flat_prior_model%>%
  filter(!(Parameter %in% c("noise_int","noise_slope")))  %>%
  separate(Parameter, into = c("age","speaker", "alignment"), sep="/")%>%
  mutate(model="flat_prior")%>%
  group_by(model,age,speaker,alignment)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))

child_ex3_flat_prior_model_noise <- child_ex3_flat_prior_model %>%
  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
  group_by(Parameter)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

@@

### Plot for noise parameter

```{r visualizing noise parameters}
plot_noise_param <- data_frame(
  age = rep(seq(0,2, by = 0.05),3),
  model = c(
    rep("pragmatic",41),
    rep("prior_only",41),
    rep("flat_prior",41)),
  int = c(
    rep(child_ex3_pragm_model_noise%>%filter(Parameter=="noise_int")%>%pull(mean),41),
    rep(child_ex3_prior_only_model_noise%>%filter(Parameter=="noise_int")%>%pull(mean),41),
    rep(child_ex3_flat_prior_model_noise%>%filter(Parameter=="noise_int")%>%pull(mean),41)
    ),
  slope = c(
    rep(child_ex3_pragm_model_noise%>%filter(Parameter=="noise_slope")%>%pull(mean),41),
    rep(child_ex3_prior_only_model_noise%>%filter(Parameter=="noise_slope")%>%pull(mean),41),
    rep(child_ex3_flat_prior_model_noise%>%filter(Parameter=="noise_slope")%>%pull(mean),41)
    )
) %>%
  mutate(y = plogis(int + slope *age))

plot_child_noise_param_dev <- ggplot(plot_noise_param, aes(x = age, y= y, col = model))+
  geom_line(size = 2)+
  ylim(0,1)+
  theme_few()+
  ylab("Noise parameter")+
  scale_color_manual(name="Model",
                     breaks=c("pragmatic","flat_prior","prior_only"),
                     values= c("#859900","#6c71c4","#b58900"))

child_noise_param_by_model <- bind_rows(
  child_ex3_pragm_model%>%mutate(model="pragmatic"),
  child_ex3_prior_only_model%>%mutate(model="prior_only"),
  child_ex3_flat_prior_model%>%mutate(model="flat_prior")
) %>%
  filter(Parameter %in% c("noise_int", "noise_slope"))

plot_child_noise_param_by_model <- ggplot(child_noise_param_by_model, aes(x = value, col = model))+
  geom_density()+
  facet_grid(model~Parameter, scales = 'free')+
  theme_few()+
  scale_color_manual(name="Model",
                     breaks=c("pragmatic","flat_prior","prior_only"),
                     values= c("#859900","#6c71c4","#b58900"))

ggarrange(plot_child_noise_param_by_model, plot_child_noise_param_dev, common.legend = T)
```

@@

ggplot(child_model_predictions)+
  #geom_jitter(data = plot_child_ex3_data, aes(x = age_num, y = mean), width = .025,height = .025, alpha = .2)+
  geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
  geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 1.5,  se = T,  alpha = .5)+
  #geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  ylim(-0.05,1.05)+
  facet_grid(speaker~alignment)+
  theme_few()+
  scale_color_manual(name="Model",
                     breaks=c("pragmatic","flat_prior","prior_only"),
                     values= c("#859900","#6c71c4","#b58900"))+
  scale_fill_manual(name="Model",
                     breaks=c("pragmatic","flat_prior","prior_only"),
                     values= c("#859900","#6c71c4","#b58900"))

@@

child_cor_model <- child_model_predictions %>%
  mutate(age = ifelse(age<4,"3","4"))%>%
  group_by(model,speaker,alignment, age)%>%
  summarise(Model = mean(mean),
            Model_ci_lower =hdi_lower(mean) ,
            Model_ci_upper = hdi_upper(mean))

@@

ggplot(data = child_cor_plot,aes(x = Model, y = Data, col = age)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(size = 3)+
  geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
  geom_errorbarh(aes(xmin = Model_ci_lower, xmax = Model_ci_upper), height = 0,size = .5)+
  coord_fixed()+
  facet_grid(~model)+
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = Model, y = Data), inherit.aes = F)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  theme_few() + 
  scale_colour_ptol()
```

>>>>

@@

@@

    return extend([row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(modelPredictions.score(1))])

@@

output

```{r}
child_ex3_pragm_model<- webppl(
  program_code = paste(rsaUtils, childRsaModel, child.ex3.rsa.predictions , sep='\n'),
  data =list(ex3data = ex3_model_data),
  data_var = "dataFromR"
)

# model predictions
child_ex3_pragm_model_predictions <- child_ex3_pragm_model %>%
  separate(`0`, into = c("age", "speaker", "alignment"), sep="/")%>%
  mutate(value = `1`,
         model="pragmatic",
         age = as.numeric(age))%>%
  select(-`1`)
```

@@

 output

```{r}
child_ex3_prior_only_model<- webppl(
  program_code = paste(rsaUtils, childRsaModel, child.ex3.prior.only.predictions , sep='\n'),
  data =list(ex3data = ex3_model_data),
  data_var = "dataFromR"
)

# model predictions
child_ex3_prior_only_model_predictions <- child_ex3_prior_only_model %>%
  separate(`0`, into = c("age", "speaker", "alignment"), sep="/")%>%
  mutate(value = `1`,
         model="prior_only",
         age = as.numeric(age))%>%
  select(-`1`)

@@

output

```{r}
child_ex3_flat_prior_model<- webppl(
  program_code = paste(rsaUtils, childRsaModel, child.ex3.flat.prior.predictions , sep='\n'),
  data =list(ex3data = ex3_model_data),
  data_var = "dataFromR")

# model predictions
child_ex3_flat_prior_model_predictions <- child_ex3_flat_prior_model %>%
  separate(`0`, into = c("age", "speaker", "alignment"), sep="/")%>%
  mutate(value = `1`,
         model="flat_prior",
         age = as.numeric(age))%>%
  select(-`1`)

@@

@@

ggplot(child_model_predictions)+
  #geom_jitter(data = plot_child_ex3_data, aes(x = age_num, y = mean), width = .025,height = .025, alpha = .2)+
  geom_line(aes(x = age, y = value, col = model), size = 1, alpha = 1, linetype = 1) + 
  geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 1.5,  se = T,  alpha = .5)+
  #geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  ylim(-0.05,1.05)+
  facet_grid(speaker~alignment)+
  theme_few()+
  scale_color_manual(name="Model",
                     breaks=c("pragmatic","flat_prior","prior_only"),
                     values= c("#859900","#6c71c4","#b58900"))+
  scale_fill_manual(name="Model",
                     breaks=c("pragmatic","flat_prior","prior_only"),
                     values= c("#859900","#6c71c4","#b58900"))

@@

child_cor_model <- child_model_predictions %>%
  mutate(age = ifelse(age<4,"3","4"))%>%
  group_by(model,speaker,alignment, age)%>%
  summarise(Model = mean(value))

@@

ggplot(data = child_cor_plot,aes(x = Model, y = Data, col = age)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(size = 3)+
  geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
  coord_fixed()+
  facet_grid(~model)+
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = Model, y = Data), inherit.aes = F)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  theme_few() + 
  scale_colour_ptol()
```

### 2019-03-09 stats/kids/kids_model_predictions.Rmd
clean version models with non parametric model predictions for kids

plot_inf <- ggplot(data = pre_so, aes(x = age_num, y = correct)) +
  geom_jitter(alpha = 1, height = 0.1, width = 0.1, col = "grey")+
  geom_smooth(method = "lm", se = T, col = "black",fill = "darkgreen", alpha = .4, size = .4)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="age",y="Proportion Expected Choice")+
  theme_few() +
  ggtitle("Informativeness data")+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  coord_fixed(ratio = 2)
```

@@

var model  = function(){
  var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
  var so_int = uniformDrift({a: -2, b: 2, width: 0.4})
  foreach(function(row){
    var age = row.age_num
    var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)

@@

```{r}
params_by_age<- readRDS("../saves/child_model_param.rds")

params_by_age<- webppl(
  program_code = paste(rsaUtils, rsaModel, paramModelWebppl , sep='\n'),
  data = pre_data,
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 2000, burn = 200, verbose = T)
)

@@

@@

@@

```{r}
modelPredWebppl <- '

@@

model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, modelPredWebppl , sep='\n'),
  data = list(ex3data = ex3_data_param, modelParams = model_params),
  data_var = "dataFromR"
)

@@

pred <- model_pred %>%
  gather(condition, mean, -age_bin)%>%
  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"),
         model = "parameter free", 
         age = age_bin+3)%>%
  select(-age_bin)
```

@@

ex3_data_param <- ex3_data%>%
  mutate(different_speaker_pref_int = model_params$different_speaker_pref_int,
         different_speaker_pref_slope = model_params$different_speaker_pref_slope,
         so_int = model_params$NA_so_int,
         so_slope = model_params$NA_so_slope,
         same_speaker_pref_int = model_params$same_speaker_pref_int,
         same_speaker_pref_slope = model_params$same_speaker_pref_slope,
         so = so_int+so_slope*(age_num-min(age_num)),
         diff_prior = plogis(different_speaker_pref_int+different_speaker_pref_slope*(age_num-min(age_num))),
         same_prior = plogis(same_speaker_pref_int+same_speaker_pref_slope*(age_num-min(age_num))))%>%
  group_by(subid,trial)%>%
        mutate(priorProbs = ifelse(Speaker == "same_speaker" & Alignment == "congruent", list(c(1-same_prior,1-same_prior,same_prior)),
                                   ifelse(Speaker == "different_speaker" & Alignment == "congruent", list(c(1-diff_prior,1-diff_prior,diff_prior)),
                                          ifelse(Speaker == "same_speaker" & Alignment == "incongruent", list(c(same_prior,same_prior,1-same_prior)),
                                                 list(c(diff_prior,diff_prior,1-diff_prior))

@@

models <- bind_rows(
  pred,
  noisy_pred,
  dev_noisy_pred
)

@@

ggplot(models)+
  #geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
  geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
  geom_smooth(data = p_data, aes(x = age_num, y = correct_inf), col = "black", method = "loess", span = 1, se = T,  alpha = .5, size = .4)+
  #geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  ylim(-0.05,1.05)+
  facet_grid(Speaker~Alignment)+
  theme_few()+
  scale_color_solarized()+
  scale_fill_solarized()

@@

cor_plot <- model %>%
  ungroup()%>%
  mutate(Data = rep(data$Data,3),
         Data_ci_lower = rep(data$Data_ci_lower,3),
         Data_ci_upper  =rep( data$Data_ci_upper,3))

>>>>

plot_inf <- ggplot(data = pre_so, aes(x = age_num, y = correct)) +
  geom_jitter(alpha = 1, height = 0.1, width = 0.1, col = "grey")+
  geom_smooth(method = "lm", formula = y ~ x + I(x^2), se = T, col = "black",fill = "darkgreen", alpha = .4, size = .4)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="age",y="Proportion Expected Choice")+
  theme_few() +
  ggtitle("Informativeness data")+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  coord_fixed(ratio = 2)
```

@@

var model  = function(){
  var so_slope = uniformDrift({a: -3, b: 3, width: 0.4})
  var so_slope_quad = uniformDrift({a: -3, b: 3, width: 0.4})
  var so_int = uniformDrift({a: -3, b: 3, width: 0.4})

  foreach(function(row){
    var age = row.age_num
    var speakerOptimality = so_int  + so_slope * (age - infData[0].minage) + so_slope_quad * Math.pow((age - infData[0].minage),2)

  return _.flatten(pref_params).concat(
    [
      {condition: "NA", param: "so_slope", val: so_slope},
      {condition: "NA", param: "so_slope_quad", val: so_slope_quad},
      {condition: "NA", param: "so_int", val: so_int}
    ]
  )
}
'
```

```{r}
linParamModelWebppl <- '

var model  = function(){
  var so_slope = uniformDrift({a: -3, b: 3, width: 0.4})
  var so_slope_quad = uniformDrift({a: -3, b: 3, width: 0.4})
  var so_int = uniformDrift({a: -3, b: 3, width: 0.4})

  foreach(function(row){
    var age = row.age_num
    var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)

@@

```{r}
params_by_age<- webppl(
  program_code = paste(rsaUtils, rsaModel, paramModelWebppl , sep='\n'),
  data = pre_data,
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples =2000, burn = 1000, verbose = T)
)

@@

so_plot <- child_ex1_data %>%
  group_by(id,age_num,minage)%>%
  summarise(correct = mean(correct))%>%
  mutate(model = model_params$NA_so_int + model_params$NA_so_slope * (age_num - minage) + model_params$NA_so_slope_quad * (age_num - minage)^2)

ggplot(data = so_plot, aes(x = age_num, y = model)) +
  geom_line(alpha = .5, size = .7)+
  labs(x="Age",y="Speaker optimality parameter")+
  theme_few() +
  geom_hline(yintercept = 0, lty=2)+
  ylim(-3,3)+
  guides(alpha = F)

# linear parameters

lin_params_by_age<- webppl(
  program_code = paste(rsaUtils, rsaModel, linParamModelWebppl , sep='\n'),
  data = pre_data,
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples =2000, burn = 1000, verbose = T)
)

lin_model_params <- lin_params_by_age%>%
  select(value) %>%
  map_df(bind_rows)%>%
  group_by(condition,param)%>%
  summarise(param_map = estimate_mode(val))%>%
  mutate(cond = paste(condition, param, sep = "_"))%>%
  ungroup()%>%
  select(cond,param_map)%>%
  spread(cond,param_map)

lin_so_plot <- child_ex1_data %>%
  group_by(id,age_num,minage)%>%
  summarise(correct = mean(correct))%>%
  mutate(model = lin_model_params$NA_so_int + lin_model_params$NA_so_slope * (age_num - minage))

ggplot(data = lin_so_plot, aes(x = age_num, y = model)) +
  geom_line(alpha = .5, size = .7)+
  labs(x="Age",y="Speaker optimality parameter")+
  theme_few() +
  geom_hline(yintercept = 0, lty=2)+
  ylim(-3,3)+
  guides(alpha = F)

@@

```{r}
plot_model_pred_so <- kids_model_pred_so%>%
  group_by(age_bin)%>%
  summarise(mean = mean(speakerOptimality),
            lci = hdi_lower(speakerOptimality),
            uci = hdi_upper(speakerOptimality))

pred_so_plot <- ggplot(data = plot_model_pred_so) +
  geom_line(data = kids_model_pred_so,aes(age_bin, speakerOptimality, group = iteration), col = "grey", alpha = 0.3) +
  geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci), fill = "green", alpha = .2) +
  geom_line(aes(age_bin, mean), col = "black", size = 0.4, alpha = 1) + 
  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
  scale_y_continuous(limits=c(-4, 4), name="Speaker optimality")+
  ggtitle("Speaker optimality model")+
  #facet_wrap(~chain)+
  theme_few()+
  coord_fixed(ratio=1/4)
```

@@

```{r}
linModelPredWebppl <- '

@@

lin_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, linModelPredWebppl , sep='\n'),
  data = list(ex3data = ex3_data_param, modelParams = lin_model_params),
  data_var = "dataFromR"
)

@@

lin_pred <- lin_model_pred %>%
  gather(condition, mean, -age_bin)%>%
  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"),
         model = "pragmatic_linear", 
         age = age_bin+3)%>%
  select(-age_bin)
```

```{r}
linFlatModelPredWebppl <- '

    var diff_priorProbs_congruent = [0.5, 0.5, 0.5]

    var diff_priorProbs_incongruent = [0.5, 0.5, 0.5]

    var same_priorProbs_congruent = [0.5, 0.5, 0.5]

    var same_priorProbs_incongruent = [0.5, 0.5, 0.5]

model_pred_flat_lin <- webppl(
  program_code = paste(rsaUtils, rsaModel, linFlatModelPredWebppl , sep='\n'),
  data = list(ex3data = ex3_data_param, modelParams = model_params),
  data_var = "dataFromR"
)

lin_flat_pred <- model_pred_flat %>%
  gather(condition, mean, -age_bin)%>%
  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"),
         model = "flat_prior", 
         age = age_bin+3)%>%
  select(-age_bin)
```

```{r}
linPriorModelPredWebppl <- '

    var rsaPredictions_diff_cong =  Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: diff_priorProbs_congruent}));
      return obj.shape == "circle" ? 1 : 0
       }})

    var rsaPredictions_diff_incong =Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: diff_priorProbs_incongruent}));
      return obj.shape == "circle" ? 1 : 0
       }})

    var rsaPredictions_same_cong = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: diff_priorProbs_incongruent}));
      return obj.shape == "circle" ? 1 : 0
       }})

    var rsaPredictions_same_incong = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: same_priorProbs_incongruent}));
      return obj.shape == "circle" ? 1 : 0
       }})

   var predictions_diff_cong  =   Math.exp(rsaPredictions_diff_cong.score(1))
   var predictions_diff_incong  =   Math.exp(rsaPredictions_diff_incong.score(1))
   var predictions_same_cong  =   Math.exp(rsaPredictions_same_cong.score(1))
   var predictions_same_incong  =   Math.exp(rsaPredictions_same_incong.score(1))

  return extend(
      {predictions_diff_cong,
      predictions_diff_incong,
      predictions_same_cong,
      predictions_same_incong,
      age_bin
    })

lin_model_pred_prior<- webppl(
  program_code = paste(rsaUtils, rsaModel, linPriorModelPredWebppl , sep='\n'),
  data = list(ex3data = ex3_data_param, modelParams = lin_model_params),
  data_var = "dataFromR"
)

lin_pred_prior <- lin_model_pred_prior %>%
  gather(condition, mean, -age_bin)%>%
  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"),
         model = "prior_only", 
         age = age_bin+3)%>%
  select(-age_bin)

@@

ex3_data_param <- ex3_data%>%
  mutate(different_speaker_pref_int = model_params$different_speaker_pref_int,
         different_speaker_pref_slope = model_params$different_speaker_pref_slope,
         so_int = model_params$NA_so_int,
         so_slope = model_params$NA_so_slope,
         so_slope_quad = model_params$NA_so_slope_quad,
         same_speaker_pref_int = model_params$same_speaker_pref_int,
         same_speaker_pref_slope = model_params$same_speaker_pref_slope,
         so = so_int+so_slope*(age_num-min(age_num))+so_slope_quad*(age_num-min(age_num))^2,
         diff_prior = plogis(different_speaker_pref_int+different_speaker_pref_slope*(age_num-min(age_num))),
         same_prior = plogis(same_speaker_pref_int+same_speaker_pref_slope*(age_num-min(age_num))))%>%
  group_by(subid,trial)%>%
        mutate(priorProbs = ifelse(Speaker == "same_speaker" & Alignment == "congruent", list(c(1-same_prior,1-same_prior,same_prior)),
                                   ifelse(Speaker == "different_speaker" & Alignment == "congruent", list(c(1-diff_prior,1-diff_prior,diff_prior)),
                                          ifelse(Speaker == "same_speaker" & Alignment == "incongruent", list(c(same_prior,same_prior,1-same_prior)),
                                                 list(c(diff_prior,diff_prior,1-diff_prior))

@@

models <- bind_rows(
  quad_pred,
  lin_pred,
  lin_flat_pred,
  lin_pred_prior
)

@@

ggplot(models)+
  #geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
  #geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
  geom_smooth(data = p_data, aes(x = age_num, y = correct_inf), col = "black", method = "loess", span = 2, se = T,  alpha = .5, size = .4)+
  #geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  ylim(-0.05,1.05)+
  facet_grid(Speaker~Alignment)+
  theme_few()+
  scale_color_solarized()+
  scale_fill_solarized()

@@

cor_plot <- model %>%
  ungroup()%>%
  mutate(Data = rep(data$Data,4),
         Data_ci_lower = rep(data$Data_ci_lower,4),
         Data_ci_upper  =rep( data$Data_ci_upper,4))
